\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2020-03-16 sections/results.tex

  To compare the representative sequences generated by these methods we employ both the weighted~\cite{Lozupone2007} (Figure~\ref{fig:figure3}A) and unweighted UniFrac method~\cite{Lozupone2005} (Figure~\ref{fig:figure3}B).
  The weighted UniFrac distance metric takes into account the counts of the representative sequences, whereas the unweighted UniFrac distance metric does not and hence gives equal weights to each sequence.
  From Figure~\ref{fig:figure3}A we can observe that the representative sequences generated by the different methods are similar to each other when weighted by their abundance.
  Figure~\ref{fig:figure3}B on the other hand shows an increase in dissimilarity between each pair of methods suggesting that the methods might differ in the sequences of low abundance.
  In order to verify this claim, we changed the threshold for the sequence count and recalculated the weighted and unweighted UniFrac distance metrics and also looked at the number of representative sequences identified in each case (in the supplementary section).

  %% TODO: Check if this is necessary
    % For each of these methods we use the same taxonomy database (\ac{gg}) to assign taxonomies to the representative sequences.
    % We then correlate the abundances of matching taxonomies between every combination of a pair of methods (Figure \ref{fig:all_denoise_reg}).
    % The \ac{esv} tables generated by methods that perform denoising are very similar to each other $\sim0.9$ and the \ac{otu} tables generated by the clustering methods are very similar to each other $\sim0.9$, but results of denoising and clustering are highly uncorrelated with each other $\sim0.4$ (Figure \ref{fig:figureS2}).
    % The common core network (network made up of edges that are predicted by all methods) is very small compared to the total number of edges predicted by all the methods (Figure \ref{fig:denoise_network}).
    % In these results, only the denoising method was changed (database used: \ac{gg} and network inference: \ac{sparcc}).

@@

  % TODO: Check if this is necessary
    % Figure~\ref{fig:figureS3} shows that the top 20 most abundant genera in the three resulting taxonomy composition tables are different.
    % The most abundant genus in the \ac{gg} taxonomy table was \textit{Escherichia} whereas in the SILVA taxonomy table it was \textit{Escherichia-Shigella}.
    % These might seem like minor differences, but when comparing a large number of composition tables these problems are hard to diagnose.
    % Figure~\ref{fig:tax_comparison_all} shows that the result is very similar when you look at all genera instead of just the top 20 most abundant genera.
    % Moreover, Figure~\ref{fig:venn_tax} shows that there does not seem to exist a correlation between abundance and mismatch.
    % This implies that the most abundant sequences are not necessarily the ones that are consistently matched to the same taxonomies in the different reference databases.

>>>>

  To compare the representative sequences generated by these methods we employ both the weighted~\cite{Lozupone2007} (Figure~\ref{fig:figure3}A) and unweighted UniFrac method~\cite{Lozupone2005} (Figure~\ref{fig:figure3}B).
  The weighted UniFrac distance metric takes into account the counts of the representative sequences, whereas the unweighted UniFrac distance metric does not and hence gives equal weights to each sequence.
  From Figure~\ref{fig:figure3}A we can observe that the representative sequences generated by the different methods are similar to each other when weighted by their abundance.
  Figure~\ref{fig:figure3}B on the other hand shows an increase in dissimilarity between each pair of methods suggesting that the methods might differ in the sequences of low abundance.
  %% TODO: Update this
  In order to verify this claim, for each of these methods we use the \ac{gg} taxonomy database to assign taxonomies to the representative sequences.
  We then correlate the abundances of matching taxonomies between a pair of DC methods (Figure \ref{fig:figureS1}A and B).
  The \ac{esv} tables generated by methods that perform denoising are very similar to each other $\sim0.91$ and the \ac{otu} tables generated by the clustering methods are very similar to each other $\sim0.9$, but results of denoising and clustering are highly uncorrelated with each other $\sim0.4$ (Figure \ref{fig:figureS1}C).
  % The common core network (network made up of edges that are predicted by all methods) is very small compared to the total number of edges predicted by all the methods (Figure \ref{fig:denoise_network}).
  % In these results, only the denoising method was changed (database used: \ac{gg} and network inference: \ac{sparcc}).

@@

  % TODO: Update this
  Figure~\ref{fig:figureS4} shows that the top 20 most abundant genera in the three resulting taxonomy composition tables are different.
  For example, the most abundant genus in the \ac{gg} taxonomy table was \textit{Escherichia} whereas in the SILVA taxonomy table it was \textit{Escherichia-Shigella}.
  Although these are minor differences, when comparing a large number of composition tables these problems are hard to diagnose.
  The comparison of all assigned genera instead of the just the top 20 contains the same percentage of matches and mismatches, implying that there does not seem to exist a correlation between abundance and mismatch.
  This suggests that the most abundant sequences are not necessarily the ones that are consistently matched to the same taxonomies in the different reference databases.
